Algebraic Tori in Unitary Groups

### 2014-03-22 Paper.tex
Added references file, made some changes

\documentclass{article}
\usepackage{amsmath,amscd,amssymb,latexsym, amsfonts}
%\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{xypic}

@@

@@

\TODO{} Decide which of the following to define/give notations for, we probably don't need all of it. Some of it can be postponed until the sections where it is used.
\begin{itemize}
\item The setting is a base field $K$ taken to be a $p$-adic field or number field (should we notationally distinguish? I don't currently).
\item We shall denote by $...$ the absolute Galois group of $K$.
\item \'Etale algebras are... typically denoted by $E$.
\item \'Etale algebras with involutions are...
\item Algebraic Tori are... 
\item Hermitian Spaces are ... their invariants over (local fields, global fields) are...
\item Unitary groups are ... their invariants over (local fields, global fields) are...
\item Quadratic Forms are ...their invariants over (local fields, global fields) are...
\item Orthogonal Groups are ...their invariants over (local fields, global fields) are...
\item Connections between orthogonal and unitary groups.
\end{itemize}

@@

Let $T$ be a torus defined over $K$ and $\rho:T_K \rightarrow \GL(V_K)$ a $K$-rational algebraic representation of $T$ (one can and might as well assume $\rho$ is injective).

Associated to this data there exists an \'etale algebra $E$ over $K$, inclusions $\rho'' : E \hookrightarrow \End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.

@@

\begin{notation}
Given an \'etale algebra with involution $(E,\sigma)$ of dimension $2n$ and $\lambda \in (E^\sigma)^\times$ let $z\in E^\sigma$ be such that $\sqrt{z}$ primitively generates $E$ over $K$ and denote by $f'_z(X)$ its minimal polynomial.
Define the Hermitian form:
\[ H_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/A}\left(\lambda x\sigma(y)\right) \]
and the symmetric bilinear form:
\[ B_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/A}\left(\lambda x\sigma(y)\right). \]
\end{notation}

>>>>

\documentclass{article}
\usepackage{amsmath,amscd,amssymb,latexsym, amsfonts}
%\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{xypic}
\usepackage{yfonts, mathrsfs}

@@

\newcommand{\aK}{K}
\newcommand{\gK}{\mathcal{K}}
\newcommand{\lK}{\mathfrak{K}}
\newcommand{\fK}{\textswab{K}}
\newcommand{\aL}{L}
\newcommand{\gL}{\mathcal{L}}
\newcommand{\lL}{\mathfrak{L}}
\newcommand{\fL}{\textswab{L}}
\newcommand{\aE}{E}
\newcommand{\gE}{\mathcal{E}}
\newcommand{\lE}{\mathfrak{E}}
\newcommand{\fE}{\textswab{E}}
\newcommand{\aV}{V}
\newcommand{\gV}{\mathcal{V}}
\newcommand{\lV}{\mathfrak{V}}
\newcommand{\fV}{\textswab{V}}

@@

\TODO{} Decide which of the following to define/give notations for, we probably don't need all of it. Some of it can be postponed until the sections where it is used.
\begin{itemize}
\item Explain our notation for fields and \'etale algebras: $\aK$, $\gK$, $\lK$, $\fK$, $\aL$, $\gL$, $\lL$, $\fL$, $\aE$, $\gE$, $\lE$, $\fE$, $\aV$, $\gV$, $\lV$, $\fV$.
\item The setting is a base field $K$ taken to be a $p$-adic field or number field (should we notationally distinguish? I don't currently).
\item We shall denote by $...$ the absolute Galois group of $K$.
\item \'Etale algebras are... typically denoted by $E$.
\item \'Etale algebras with involutions are...
\item Algebraic Tori are... 
\item Hermitian Spaces are ... their invariants over (local fields, global fields) are...
\item Unitary groups are ... their invariants over (local fields, global fields) are...
\item Quadratic Forms are ...their invariants over (local fields, global fields) are...
\item Orthogonal Groups are ...their invariants over (local fields, global fields) are...
\item Connections between orthogonal and unitary groups.
\end{itemize}

@@

Let $T$ be a torus defined over $\aK$, $\aV$ a vector space over $\aK$ and $\rho:T_\aK \rightarrow \GL(V)$ an injective $\aK$-rational algebraic representation of $T$.

Associated to this data there exists an \'etale algebra $\aE$ over $\aK$, inclusions $\rho'' : \aE \hookrightarrow \End(V_K)$ and $\rho' : T \rightarrow T_E$ for which $\rho = \rho''\circ\rho'$.

@@

\begin{notation}
Given an \'etale algebra with involution $(E,\sigma)$ of dimension $2n$ and $\lambda \in (E^\sigma)^\times$ let $z\in E^\sigma$ be such that $\sqrt{z}$ primitively generates $E$ over $K$ and denote by $f'_z(X)$ its minimal polynomial.
Define the Hermitian form:
\[ H_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/A}\left(\lambda x\sigma(y)\right) \]
and the symmetric bilinear form:
\[ B_{E,\sigma,\lambda} := \tfrac{1}{2}Tr_{E/K}\left(\lambda x\sigma(y)\right). \]
\end{notation}
